

针对现有多租户云无法保障租户网络性能的问题，提出一种多租户云的内部网络共享策略FairNet。该策略在最小保证、公平分配、最大利用三个目标之间取得平衡,分别在主机上实现最小保证和最大利用，在交换机链路上实现公平分配和最大利用；确保在主机上每个虚拟机能够分配到一个最小带宽，并且主机的剩余带宽被需要的虚拟机共享；估计交换机链路上租户的带宽需求以计算权重，而交换机链路按照权重的比例分配带宽。在NS-3仿真器上进行了实验，实验结果表明,与其它的算法相比，FairNet能够更好的适应不同的通信模式，且FairNet的网络公平性仅次于PS-N，但是计算成本却比PS-N小得多。

An intra-network sharing policy named FairNet is proposed to solve the problem that existing multi-tenant clouds are unable to protect network performance for tenants. The policy balances three targets, including minimum guarantee, equitable allocation, and maximum utilization. Hosts implement minimum guarantee and maximum utilization, while links of switches achieve equitable allocation and maximum utilization. In a host, every virtual machine is promised a minimal bandwidth, and the idle bandwidth is shared by the virtual machines on demand. In a link of a switch, the bandwidth is allocated on the proportion of weights, which are computed by estimating the bandwidth demands of tenants. Experiments are conducted on the NS-3 simulator, and the results show that, compared with other algorithms, FairNet can adapt better to different communication patterns. Besides, the network fairness of FairNet is the second best after PS-N, but the calculation cost FairNet paid is much smaller.

An intra-network sharing policy, FairNet, is proposed to solve the problem that existing multi-tenant clouds can not guarantee/provide a great network performance. The proposed policy balances three targets, including minimum guarantee, equitable allocation, and maximum utilization. In the host, we attain/get the minimum guarantee and the maximum utilization, while links of switches achieve equitable allocation and maximum utilization. In a host, every virtual machine obtains a minimal bandwidth, and the remaining idle bandwidth is shared by the virtual machines on demand. In a link of a switch, the bandwidth is allocated on the proportion of weights, which are computed by estimating the bandwidth demands of tenants. Experiments are conducted on the NS-3 simulator(We conduct experiments on the NS-3 simulator, the results show that ...), and the results show that FairNet can adapt better to different communication patterns than other algorithms. Besides, the network fairness of FairNet is the second best after PS-N, however the calculation cost FairNet paid is much smaller. 