
\begin{thebibliography}{}
%chap-intro-1
\bibitem{cnnic}中国互联网络信息中心. 中国互联网络发展状况统计报告~[EB/OL]. http://www.cnnic.cn/hlwfzyj/hlwxzbg/hlwtjbg/201403/P0201403053465859
    59798.pdf. 2014.
\bibitem{cloud-1}罗军舟，金嘉晖，宋爱波等. 云计算: 体系架构与关键技术[J]. 通信学报，2011，32(7) : 3－18．
\bibitem{cloud-2}陈康，郑纬民. 云计算: 系统实例与研究现状[J]. 软件学报，2009，20(5) : 1337 －1348.
\bibitem{salesforce}Salesforce[EB/OL]. http://www.salesforce.com/. 2014.
\bibitem{crm}CRM~客户关系管理[EB/OL]. http://www.salesforce.com/cn/crm/what-is-crm.jsp. 2014.
\bibitem{amazon}Amazon~[EB/OL]. http://www.amazon.com/. 2014.
\bibitem{ec2-web}Amazon EC2 [EB/OL]. https://aws.amazon.com/cn/ec2/. 2014.
\bibitem{s3}Amazon S3 [EB/OL]. http://aws.amazon.com/cn/s3/. 2014.
\bibitem{sqs}Amazon SQS [EB/OL]. http://aws.amazon.com/cn/sqs/. 2014.
\bibitem{gae-1}Google App Engine [EB/OL]. http://code.google.com/appengine/. 2014.
\bibitem{gae-2}A. Zahariev, Google App Engine, in TKK T-110.5190 Seminar on Internetworking, 2009, pp. 1-5.
\bibitem{ma}MicroSoft Azure [EB/OL]. http://www.microsoft.com/windowsazure/. 2014.
\bibitem{openstack}OpenStack [EB/OL]. http://www.openstack.org/. 2014.
\bibitem{eucalyptus-1}D. Nurmi, R. Wolski, C. Grzegorczyk, G. Obertelli, S. Soman, L. Youseff, and D. Zagorodnov. The Eucalyptus Open-Source Cloud-Computing System [C]. In Cloud Computing and Applications 2008 (CCA08), 2008.
\bibitem{eucalyptus-2}Eucalyptus [EB/OL]. http://www.eucalyptus.com/. 2014.
\bibitem{opennebula}OpenNebula [EB/OL]. http://opennebula.org/. 2014.
\bibitem{cloudstack}CloudStack [EB/OL]. http://incubator.apache.org/cloudstack/. 2014.

%chap-relate-2
\bibitem{cloud1}R. Buyya, C. S. Yeo, and S. Venugopal. Market-oriented cloud computing: Vision, hype, and reality for delivering it services as computing utilities[C]. In Proc. 10th IEEE Int. Conf. High Performance Computing and Communications. pp. 5-13. 2008.

\bibitem{cloud2}M. Armbrust, A. Fox, R. Griffith, A. D. Joseph, R. Katz, A. Konwinski, G. Lee, D. Patterson, A. Rabkin, I. Stoica, and M. Zaharia. Above the clouds: A Berkeley view of cloud computing[EB/OL]. EECS Dept., Univ. California, Berkeley, No. UCB/EECS-2009-28. https://radlab.cs.berkeley.edu/.

\bibitem{cas-cloud}Cloud Security Alliance. Security Guidance for Critical Areas of Focus in Cloud Computing V3.0[EB/OL]. http://www.cloudsecurityalliance.org/guidance/csaguide.v3.0.pdf. 2011.
\bibitem{nist-cloud}U.S. National Institute of Standards and Technology. NIST Working Definition of Cloud Computing/NIST 800-145[EB/OL]. http://csrc.nist.gov/publications/nistpubs/800-145/SP800-145.pdf. 2011.
\bibitem{openstack-compute}OpenStack Compute[EB/OL].
http://www.openstack.org/software/openstack-compute/. 2014.
\bibitem{nova}Nova[EB/OL]. https://github.com/openstack/nova. 2014.
\bibitem{openstack-storage}OpenStack Storage[EB/OL].
http://www.openstack.org/software/openstack-storage/. 2014.
\bibitem{openstack-shared}OpenStack Shared Services[EB/OL].
http://www.openstack.org/software/openstack-shared-services/. 2014.
\bibitem{dashboard}OpenStack Dashboard[EB/OL].
http://www.openstack.org/software/openstack-dashboard/. 2014.
\bibitem{cloud-level}Eucalyptus Cloud Level[EB/OL].
https://www.eucalyptus.com/eucalyptus-cloud/iaas/architecture/cloud-level. 2014.
\bibitem{cluster-level}Eucalyptus Cluster Level[EB/OL].
https://www.eucalyptus.com/eucalyptus-cloud/iaas/architecture/cluster-level. 2014.
\bibitem{node-level}Eucalyptus Node Level[EB/OL].
https://www.eucalyptus.com/eucalyptus-cloud/iaas/architecture/node-level. 2014.
\bibitem{vmm}S. Devine, E. Bugnion, and M. Rosenblum. Virtualization system including a virtual machine monitor for a computer with a segmented architecture[P]. US Patent, 6397242, Oct. 1998.
\bibitem{container-virtual}S. Soltesz, H. Potzl, M. E. Fiuczynski, A. Bavier, and L. Peterson. Container-based operating system virtualization: A scalable, high-performance alternative to hypervisors[C]. In Proc. EuroSys, pp. 275C287, 2007.
\bibitem{xen}Paul Barham, Boris Dragovic, Keir Fraser, Steven Hand, Tim Harris, Alex Ho, Rolf Neugebauer, Ian Pratt, and Andrew Warfield. Xen and the art of virtualization[C]. In Proceedings of the nineteenth ACM symposium on Operating Systems Principles (SOSP19), pp. 164-177. ACM Press, 2003.

%chap-vne-3
\bibitem{multi-way}D. G. Andersen. Theroretical approaches to node assignment[Z]. unpublished Manuscript. 2002.
\bibitem{unsplittable1}J. Kleinberg. Approximation algorithms for disjoint paths problems[D]. Massachusetts Institute of Technology. Ph.D. dissertation. 1996.
\bibitem{unsplittable2}S. Kolliopoulos and C. Stein. Improved approximation algorithms for upsiplitable flow problems[C]. In Proc. Foundations of Computer Science, IEEE. pp. 426-436. 1997.
\bibitem{uncoordinate}M. Yu, Y. Yi, J. Rexford, and M. Chiang. Rethinking virtual network embedding: substrate support for path splitting and migration[J]. ACM SIGCOMM Computer Communication Review. 38(2) : 17-29. 2008.
\bibitem{augmentation}N. M. M. K. Chowdhury, M. R. Rahman, and R. Boutaba. Virtual Network Embedding with Coordinated Node and Link Mapping[C]. In INFOCOM 2009, IEEE. pp. 783-791. 2009.
\bibitem{matrix}W. Cong, S. Shanbhag, and T. Wolf. Virtual network mapping with traffic matrices[C]. In Communications (ICC), 2012 IEEE International Conference on, pp. 2717-2722. 2012.
\bibitem{opportunity}S. Zhang, Z. Qian, J. Wu, S. Lu, and L. Epstein. Virtual Network Embedding with Opportunistic Resource Sharing[J]. Parallel and Distributed Systems, IEEE Transactions on, pp. 1-1. 2013.
\bibitem{svrvivable}M. Rahman and R. Boutaba. SVNE: Survivable Virtual Network Embedding Algorithms for Network Virtualization[J]. Network and Service Management, IEEE Transactions on, pp. 1-14. 2013.
\bibitem{vne-survey}A. Fischer, J. Botero, M. Beck, H. De Meer, and X. Hesselbach. Virtual Network Embedding: A Survey[J]. Communications Surveys \& Tutorials, IEEE. pp. 1-19. 2013.
%19
\bibitem{VNRe}I. Fajjari, N. Aitsaadi, G. Pujolle, and H. Zimmermann. VNR algorithm: A greedy approach for virtual networks reconfigurations[C]. In Global Telecommunications Conference (GLOBECOM2011), 2011 IEEE. pp. 1-5. 2011.
%74
\bibitem{periodic}Y. Zhu and M. Ammar. Algorithms for assigning substrate network resources to virtual network components[C]. In INFOCOM 2006. 25th IEEE International Conference on Computer Communications. pp. 1-12. 2006.
%85,91
\bibitem{vnchange1}G. Sun, H. Yu, V. An, and L. Li. A cost efficient framework and algorithm for embedding dynamic virtual network requests[J]. Future Generation Computer Systems. 29(5) : 1265-1277. 2013.
\bibitem{vnchange2}C. Marquezan, L. Granville, G. Nunzi, and M. Brunner. Distributed autonomic resource management for network virtualization[C]. In Network Operations and Management Symposium (NOMS), 2010 IEEE. pp. 463-470. 2010.
    %83
\bibitem{snchange}Z. Cai, F. Liu, N. Xiao, Q. Liu, and Z. Wang. Virtual network embedding for evolving networks[C]. In Global Telecommunications Conference (GLOBECOM 2010), 2010 IEEE. pp. 1-5. 2010.
%81
\bibitem{poschange}M. Bienkowski, A. Feldmann, D. Jurca, W. Kellerer, G. Schaffrath, S. Schmid, and J. Widmer. Competitive analysis for service migration in vnets[C]. In Proceedings of the second ACM SIGCOMM workshop on Virtualized infrastructure systems and architecture, sser. VISA ’10. New York, NY, USA: ACM. pp.17-24. 2010.

%84
\bibitem{snsave}Z. Shun-li and Q. Xue-song. A novel virtual network mapping algorithm for cost minimizing[J]. Cyber Journals: J. Selected Areas in Telecommunications (JSAT). 02(01) : 1-9. 2011.
%74,82
\bibitem{costsave}J.~Fan and M. H.Ammar. Dynamic topology configuration in service overlay networks: A study of reconfiguration policies[C]. In INFOCOM 2006. 25th IEEE International Conference on Computer Communications. pp. 1-12. 2006.
%88,89,42,90
\bibitem{interinp1}Y. Xin, I. Baldine, A. Mandal, C. Heermann, J. Chase, and A. Yumerefendi. Embedding virtual topologies in networked clouds[C]. The 6th International Conference on Future Internet Technologies, ser. CFI ’11. New York, NY, USA: ACM. pp. 26-29. 2011.
\bibitem{interinp2}B. Lv, Z. Wang, T. Huang, J. Chen, and Y. Liu. Virtual resource organization and virtual network embedding across multiple domains[C]. In Multimedia Information Networking and Security (MINES), 2010 International Conference on, pp. 725C728. 2010.
\bibitem{interinp3}A. Leivadeas, C. Papagianni, and S. Papavassiliou. Efficient resource mapping framework over networked clouds via iterated local search based request partitioning[J]. IEEE Trans. Parallel Distrib. Syst., 99 : 1-1. 2012.
\bibitem{interinp4}I. Houidi, W. Louati, W. B. Ameur, and D. Zeghlache. Virtual network provisioning across multiple substrate networks[J]. Computer Networks, special Issue on Architectures and Protocols for the Future Internet. 55(4) : 1011-1023. 2011.
%92
\bibitem{redundant1}X. Zhang, C. Phillips, and X. Chen. An overlay mapping model for achieving enhanced qos and resilience performance[C]. In Ultra Modern Telecommunications and Control Systems and Workshops (ICUMT), 2011 3rd International Congress on, pp. 1-7. 2011.
%94,95,96
\bibitem{Qosmap1}J. Shamsi and M. Brockmeyer. Qosmap: Qos aware mapping of virtual networks for resiliency and efficiency[C]. In Globecom Workshops, 2007 IEEE. pp. 1-6. 2007.
\bibitem{Qosmap2}J. Shamsi and M. Brockmeyer. Efficient and dependable overlay networks[C]. In Parallel and Distributed Processing, 2008. IPDPS 2008. IEEE International Symposium on, pp. 1-8. 2008.
\bibitem{Qosmap3}J. Shamsi and M. Brockmeyer. Qosmap: Achieving quality and resilience through overlay construction[C]. In Internet and Web Applications and Services, 2009. ICIW ’09. Fourth International Conference on, pp. 58-67. 2009.
\bibitem{singleroute}A. Razzaq and M. Rathore. An approach towards resource efficient virtual network embedding[C]. Evolving Internet (INTERNET), 2010 Second International Conference on, pp. 68-73. 2010.
\bibitem{kroute}D. Eppstein. Finding the k shortest paths[J]. SIAM J. Comput., 28 : 652C673. 1999.
\bibitem{mcf}S. Even, A. Itai, and A. Shamir. On the Complexity of Timetable and Multicommodity Flow Problems[J]. SIAM Journal of Computing. 5 : 691-703, 1976.
\bibitem{dvine-rvine}N. M. M. K. Chowdhury, M. R. Rahman, and R. Boutaba. Virtual network embedding with coordinated node and link mapping[C]. In IEEE INFOCOM. IEEE Infocom. 2009.
\bibitem{onestage}X. Cheng, S. Su, Z. Zhang, H. Wang, F. Yang, Y. Luo, and J. Wang. Virtual network embedding through topology-aware node ranking[J]. SIGCOMM Comput. Commun. Rev., 41 : 38C47. 2011.
\bibitem{pagerank}PageRank[EB/OL]. http://en.wikipedia.org/wiki/PageRank. 2014.
\bibitem{pagerank-paper}L. Page, S. Brin, R. Motwani, and T. Winograd. The pagerank citation ranking: Bringing order to the web[R]. Stanford InfoLab, Technical Report 1999-66, 1999.

%chap-tc-4
\bibitem{linuxtc-howto}Hubert Bert, et al. Linux Advanced Routing \& Traffic Control HOWTO[EB/OL]. http://www.lartc.org/lartc.pdf. 2014.
\bibitem{linuxtc}Hubert Bert. Linux advanced routing and traffic control[C]. In Proceedings of Ottawa Linux Symposium, Ottawa, Canada, pp. 213C222. 2002.
\bibitem{fifo}K. van der Laan. FIFO and LIFO incognito. Nederlandstalige TEX Gebruikersgroep[J]. pp. 121-121, 1992.
\bibitem{pfifo}TC pfifo[EB/OL]. http://linux.die.net/man/8/tc-pfifo. 2014.
\bibitem{bfifo}TC bfifo[EB/OL]. http://linux.die.net/man/8/tc-bfifo. 2014.
\bibitem{pfifofast}TC pfifo\_fast[EB/OL]. http://linux.die.net/man/8/tc-pfifo\_fast. 2014.
\bibitem{red1}S. Floyd and V. Jacobson. Random early detection gateways for congestion avoidance[J]. Networking, IEEE/ACM Transactions on, vol. 1, pp. 397-413. 1993.
\bibitem{red2}D. Lin and R. Morris. Dynamics of random early detection[C]. In ACM SIGCOMM Computer Communication Review, pp. 127-137. 1997.
\bibitem{sfq}P. E. McKenney. Stochastic fairness queueing[C]. In INFOCOM'90, Ninth Annual Joint Conference of the IEEE Computer and Communication Societies. The Multiple Facets of Integration, IEEE. pp. 733-740. 1990.
\bibitem{tbf}S. S. V. Appala and B. Erimli. Weighted fair queuing approximation in a network switch using weighted round robin and token bucket filter[P]. Google Patents. 2005.
\bibitem{cbq}C. Fragouli, V. Sivaraman, and M. B. Srivastava. Controlled multimedia wireless link sharing via enhanced class-based queuing with channel-state-dependent packet scheduling[C]. In INFOCOM'98. Seventeenth Annual Joint Conference of the IEEE Computer and Communications Societies, IEEE. pp. 572-580. 1998.
\bibitem{htb}J. Valenzuela, A. Monleon, I. San Esteban, M. Portoles, and O. Sallent. A hierarchical token bucket algorithm to enhance QoS in IEEE 802.11: proposal, implementation and evaluation[C]. In Vehicular Technology Conference, pp. 2659-2662. 2004.


%chap-supernova-5
\bibitem{boto}Boto [EB/OL]. https://github.com/boto/boto. 2014.
\bibitem{python}M. F. Sanner. Python: a programming language for software integration and development[J]. J Mol Graph Model, vol. 17, pp. 57-61, 1999.
\bibitem{ajax}Garrett JJ. Ajax: A New Approach to Web Applications[EB/OL]. 2005. https://courses.cs.washington.edu/courses/cse490h/07sp/readings/ajax
    \_adaptive\_path.pdf. 2014.
\bibitem{java}J. Gosling. The Java language specification[M].  Addison-Wesley Professional, 2000.
\bibitem{gwt}GWT, Google Web Toolkit [EB/OL]. http://www.gwtproject.org/. 2014.
\bibitem{java.lang}Package java.lang [EB/OL]. http://docs.oracle.com/javase/7/docs/api/java
    /lang/package-summary.html. 2014.
\bibitem{java.util}Pakage java.util [EB/OL]. http://docs.oracle.com/javase/7/docs/api/java
    /util/package-summary.html. 2014.
\bibitem{jvm1}Meyer, J. and T. Downing. Java virtual machine[M]. O'Reilly \& Associates, Inc. 1997.
\bibitem{jvm2}Stark, R., J. Schmid, and E. Borger. Java and the Java Virtual Machine: definition, verification, validation[M]. Springer-Verlag. 2001.

\bibitem{jetty}Jetty [EB/OL]. http://www.eclipse.org/jetty/.
\bibitem{mulesoft}Mule [EB/OL].http://www.mulesoft.org/. 2014.
\bibitem{jibx}Sosnoski, D., JiBX: Binding XML to Java Code[EB/OL]. http://jibx.
    sourceforge.net/. 2014.
\bibitem{jdbc}Reese, G., Database Programming with JDBC and JAVA[M]. O'Reilly Media, Inc. 2000.
\bibitem{netty}Haddad, Z.T.M., Implementing a TCP hole punching NAT traversal solution for P2P applications using netty[D]. University of Stirling Masters Thesis. 2010.
\bibitem{jboss}Jamae, J. and P. Johnson. JBoss in action: configuring the JBoss application server[M]. Manning Publications Co. 2009.
\bibitem{axis2c}Axis2C [EB/OL]. http://axis.apache.org/axis2/c/core/. 2014.
\end{thebibliography}
